Military mechanization as a complex adaptive system

### 2018-07-30 paper2/paper2.tex
foo

Moreover, human beings learn not only from their own experiences, but also from observing others.
State decisionmakers are no exception. For example, the stunning success of
Coalition precision-guided munitions in the 1991 Gulf War led other states who
were not direct combatants to reform their own militaries
\citep{scobell2011chinese}. There also is no guarantee that such cognition
follows typical assumptions of bounded rationality. 
Consider Ireland: between the 1920s and 1940s, it sought to spend a
large portion of its defense budget on building a small number of
tanks. This was a near-suicidal defense posture, given Ireland's
conventional weakness relative to the United Kingdom (the main object of Irish
defense thought). Rationally, Ireland should have pursued a low-mechanization,
guerrilla defense strategy given their weakness and given that exactly such a
strategy defeated the British in the 1919-22 war of independence. However,  
tanks at the time were novel technology being implemented by the leading
European militaries, and so were seen as a prestigious signifier of a ``real'' professional
military \citep{farrell1998professionalization,farrell2001transnational}. These examples
support the larger point that perception and cognition are fundamental to
understanding mechanization. A modeling framework that explicitly represents these factors
thus would be useful.

@@

This paper's findings raise an obvious and important question: what is the
missing ``brake'' that, if included in the model, 
would hold mechanization to historical levels? Fully answering this question is
beyond the scope of this paper.

>>>>

Moreover, human beings learn not only from their own experiences, but also from observing others.
State decisionmakers are no exception. For example, the stunning success of
Coalition precision-guided munitions in the 1991 Gulf War led other states who
were not direct combatants to reform their own militaries
\citep{scobell2011chinese}. Similarly, Prussia sent military observers to the
American Civil War and incorporated insights from there into its military
doctrine \citep{scheibert2001prussian}. There also is no guarantee that such cognition
follows typical assumptions of bounded rationality. 
Consider Ireland: between the 1920s and 1940s, it sought to spend a
large portion of its defense budget on building a small number of
tanks. This was a near-suicidal defense posture, given Ireland's
conventional weakness relative to the United Kingdom (the main object of Irish
defense thought). Rationally, Ireland should have pursued a low-mechanization,
guerrilla defense strategy given their weakness and given that exactly such a
strategy defeated the British in the 1919-22 war of independence. However,  
tanks at the time were novel technology being implemented by the leading
European militaries, and so were seen as a prestigious signifier of a ``real'' professional
military \citep{farrell1998professionalization,farrell2001transnational}. These examples
support the larger point that perception and cognition are fundamental to
understanding mechanization. A modeling framework that explicitly represents these factors
thus would be useful.

@@

This paper's findings raise an obvious and important question: what is the
missing ``brake'' that, if included in the model, 
would hold mechanization to historical levels? Fully answering this question is
beyond the scope of this paper. However, an extension to the base model
provides insight that may guide future research.

In the base model, the effects of an anti-mechanization lesson (defeat by an
insurgency) only accrue to the state that suffered the defeat. In the extended
model, the effect also can accrue to other states that were not direct participants 
in the conflict. Put differently, agents can learn from the experiences of other
states rather than solely from their own. This likely is a more accurate
depiction of agent cognition because there is strong historical evidence of
states revising their military force structure in response to to the perceived
lessons of other states' wars (c.f. the discussion in section 2.2.2).

This dynamic may be sufficient to curb model mechanization to historical levels
by providing a strong countervailing positive feedback loop. In the base model,
because only the direct losing side learns from an anti-mechanization lesson,
the only way that
